D_exp_2

### 2018-08-17 experiments/D_exp_2/writeup/D_exp_2.Rmd
trying roger in D_exp_2

@@

The second set of models considered were conducted to test for main effects _in the presence of interactions involving those main effects_ (after Levy, 2018)

>>>>

```{r}
dat$Condition <- as.factor(paste(dat$Item, dat$Vagueness))
ggplot(data=dat, mapping=aes(x=Item, y=RT_log, group=Vagueness)) +
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), aspect.ratio = 1) +
  facet_wrap(~Selection) +
  stat_summary(mapping=aes(y=RT_log, x=Item, group=Vagueness, colour=Vagueness), fun.y=mean, geom="line", lwd=2) +
  geom_smooth(mapping=aes(y=RT_log, x=Item, group=Vagueness, colour=Vagueness), method="loess")
```

@@

The second set of models considered were conducted to test for main effects _in the presence of interactions involving those main effects_ (after Levy, 2018).

Testing for a main effect of X when X is a two-level factor and the model also includes a main effect of a three-level factor  and the interaction between X and Y.

Testing for a main effect of Vagueness when Vagueness is a two-level factor and the model also includes a main effect of a four-level factor Item and the interaction between Vagueness and Item.

```{r}
Item.numeric <- sapply(dat$Item, function(i) contr.sum(4)[i,])
dat$Item1 <- Item.numeric[1,]
dat$Item2 <- Item.numeric[2,]
dat$Item3 <- Item.numeric[3,]
m0 <- lm(RT_log ~ 
           Item1 + Vagueness:Item1 + 
           Item2 + Vagueness:Item2 + 
           Item3 + Vagueness:Item3 +
           Selection +
           Selection:Vagueness, 
         dat)
contrasts(dat$Item) <- contr.sum(4)
m.test <- lm(RT_log ~ 
               Item +
           Vagueness:Item1 + 
           Vagueness:Item2 + 
           Vagueness:Item3 +
           Selection +
           Selection:Vagueness, 
         dat)
m1 <- lm(RT_log ~ 
           Item1 + Vagueness:Item1 + 
           Item2 + Vagueness:Item2 + 
           Item3 + Vagueness:Item3 +
           Selection +
           Selection:Vagueness +
           Vagueness,
         dat)
m100 <- lm(RT_log ~
             Item +
             Vagueness +
             Item:Vagueness+
             Selection+
             Selection:Vagueness,
           dat)
#m1 and m100 are the same model
anova(m0,m1,test="F")
```

```{r}
Item.numeric <- sapply(dat$Item, function(i) contr.sum(4)[i,])
dat$Item1 <- Item.numeric[1,]
dat$Item2 <- Item.numeric[2,]
dat$Item3 <- Item.numeric[3,]
m3 <- lm(RT_log ~ 
           Item1 + 
           Item2 +  
           Item3 , 
         dat)
contrasts(dat$Item) <- contr.sum(4)
m4 <- lm(RT_log ~
           Item,
         dat)
# m3 and m4 are the same model
```

```{r}
Item.numeric <- sapply(dat$Item, function(i) contr.sum(4)[i,])
dat$Item1 <- Item.numeric[1,]
dat$Item2 <- Item.numeric[2,]
dat$Item3 <- Item.numeric[3,]

m.full <- lm(RT_log ~
             Item +
             Vagueness +
             Selection + 
             Item:Vagueness +
             Item:Selection + 
             Vagueness:Selection,
           dat)
m.reduced <- lm(RT_log ~
                Item1 + 
                Item2 + 
                Item3 + 
                Vagueness:Item1 + 
                Vagueness:Item2 +
                Vagueness:Item3 +
                Vagueness:Selection +
                Selection +
                Item:Selection
                ,dat  )
anova(m.reduced, m.full, test="F")
```
